Phenotypic evolution is more constrained in simpler food webs

### 2019-01-22 manuscript.tex
add Acknowledgements back to manuscript for bioRxiv submission.

\emph{Number of words}: 5069

@@

>>>>

\emph{Number of words}: 5138

@@

\section{Acknowledgements}\label{acknowledgements}

We thank the staff of Humboldt Bay National Wildlife Refuge (U.S. Fish
and Wildlife Service) for facilitating experimental logistics. For
assistance with fieldwork, we thank Ruthie Espanol and Andrew MacDonald.
For funding support, we thank the University of British Columbia (James
Robert Thompson Fellowship and Four-Year Fellowship to M.A.~Barbour),
NSERC (Discovery grant to Greg Crutsinger), and the Swiss National
Science Foundation (grant 31003A\_160671 to J. Bascompte).
